\documentclass[a4paper,11pt,oneside]{article}

\usepackage[left=1in, right=1in, bottom=1in, top=0.8in]{geometry}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{enumitem}

\pagenumbering{gobble} % Removes page numbers

\usepackage[hidelinks]{hyperref}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}
\setlist{nosep}
\sloppy

\usepackage{etoolbox}
\patchcmd{\thebibliography}
  {\settowidth}
  {\setlength{\itemsep}{0pt plus 0.1pt}\settowidth}
  {}{}
\apptocmd{\thebibliography}
  {\small}
  {}{}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\usepackage{tabularx, multicol}

\begin{document}
    \begin{center}
        \LARGE{\textbf{Your Name}}
    \end{center}

    \section*{Contact Details}
    \begin{minipage}{0.5\textwidth}
        Email: \email{name@example.com}\\
        Homepage: \href{https://example.com}{example.com}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        1 Example Street, City, Postcode\\
        DoB: YYYY-MM-DD
    \end{minipage}

    \section*{Employment}
    \begin{tabularx}{\textwidth}{lX}
         YYYY - present & Current Job Title, Current Employer \\
         YYYY - YYYY    & Previous Job Title, Previous Employer.
    \end{tabularx}

    \section*{Education}
    \begin{tabularx}{\textwidth}{lX}
         YYYY - YYYY & Ph.D. Subject, University\newline
                       Title: ``Title of your thesis''\newline
                       Supervised by Professor Example\\
         YYYY - YYYY & Masters Subject, University\newline
                       Title: ``Title of your thesis''\newline
                       Supervised by Professor Example\\
         YYYY - YYYY & Undergraduate Subject, University\newline
                       Qualification\\
        \multicolumn{2}{l}{\textbf{Awards and Scholarshops} }\\
        YYYY - YYYY & \textit{Academic Achievement Scholarship} - Scholarship criteria explanation.
    \end{tabularx}

    \section*{Research}
    I have published NUMBER research papers, including publications in [examples of top journals in the field].

    \noindent\textbf{Selected highlights:}
    \begin{itemize}
        \item Awarded best paper award at conference.
        \item Joint lead author on paper in top journal.
        \item Established collaboration with notable research lab.
        \item Regular reviewer for top publication venues, including [top journals].
    \end{itemize}

    \noindent\textbf{Funding:}
    I have developed my grant-writing experience in recent years, and led the submission of a proposal to FUNDING BODY on SUBJECT, which is currently under review.
    I have also secured funding for and led the following projects:
    \begin{tabularx}{\textwidth}{p{3.2cm}X}
        YYYY\newline
        NAME (£amount) & Brief explanation\\
        YYYY - YYYY\newline
        NAME (£amount) & Brief explanation\\
    \end{tabularx}

    \section*{Key Skills}
    \begin{minipage}{0.5\textwidth}
        \begin{itemize}
            \item List your key skills here
            \item
        \end{itemize}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \begin{itemize}
            \item Do it in two columns to save space
            \item
        \end{itemize}
    \end{minipage}

    \section*{Teaching}
    I am an [Associate/Senior] Fellow of the UK Higher Education Academy (HEA).
    I have been eager to gain teaching experience alongside my primary research activities.
    So far this has involved:
    \begin{description}
        \item[Project supervision] I co-supervised the Ph.D. projects for two students (both successfully completed).
        I have supervised [funded student research projects].
        I have supervised [X] masters and [Y] undergraduate dissertation projects.
        \item[Lectures] I have given lectures for [MODULES] which contained [X] students.
    \end{description}

    \section*{Referees}
    Professor Example is head of the [Research] group at the University of Example, and my current line manager.
    Dr. Example is a senior lecturer at the University of Example, my former line manager, and PI on [the research project where I worked].\\[1em]

    \begin{minipage}{0.5\textwidth}
        Professor Example\\*
        Department of Research\\*
        University of Example\\*
        Address line 1\\*
        City, Postcode\\*
        Country\\

        \email{professor.example@example.com}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
      Dr. Example\\*
      Department of Research\\*
      University of Example\\*
      Address line 1\\*
      City, Postcode\\*
      Country\\

      \email{dr.example@example.com}
    \end{minipage}

    \clearpage
    \nocite{*}
    \renewcommand{\refname}{}
    \section*{Publications}
    % These will automatically be sorted by year, with newest at the top.
    % You will need to manually bold the titles of top venues in the bibtex file.
    Papers published at CORE A/A* venues are highlighted in bold.
    \titleformat{\section}{}{}{}{}
    \vspace{-3em}
    \bibliographystyle{plainyr-rev}
    \bibliography{publications.bib}

\end{document}
